The forestecology R package for fitting and assessing neighborhood models of the effect of interspecific competition on the growth of trees

### 2021-03-09 paper/forestecology.Rmd
About to start slash & burn 712 words

# Set output width
options(
  width = 72, 
  # Decimal precision
  digits = 3, 
  # Number of rows for tibble printing
  tibble.print_max = 5, 
  tibble.print_min = 5
)

# Resolve conflicts in function names
filter <- dplyr::filter
select <- dplyr::select
```

@@

```{r load-packages}
library(tidyverse)
library(lubridate)
library(sf)
library(patchwork)
library(forestecology)
library(blockCV)
```

@@

<!--Hack alert. I can't figure out how to ensure output of print stay within 72 character line limit-->
```{r}
comp_bayes_lm_scbi
```

>>>>

# Set output width
options(
  width = 72, 
  # Decimal precision
  digits = 3, 
  # Number of rows for tibble printing
  tibble.print_max = 5, 
  tibble.print_min = 5
)
```

@@

```{r load-packages}
library(tidyverse)
library(lubridate)
library(sf)
library(patchwork)
library(forestecology)
library(blockCV)

# Resolve conflicting functions
filter <- dplyr::filter
select <- dplyr::select
```

@@

```{r}
comp_bayes_lm_scbi
```
